Title: Invasive chameleons released from predation display more conspicuous colours

### 2022-01-22 ms_Nature.Rmd
color in title

---
title: "Title: Invasive chameleons released from predation display more conspicuous colors"
bibliography: supp_refs.bib
csl: nature.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Title: Invasive chameleons released from predation display more conspicuous colours"
bibliography: supp_refs.bib
csl: nature.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---
